Expert-In-The-Loop Causal Discovery: \\ Iterative Model Refinement Using Expert Knowledge

### 2025-06-11 paper/main.tex
small fixes

\begin{algorithm}[h]
\DontPrintSemicolon
\SetAlgoLined
\SetKwFunction{Expand}{Expand}
\SetKw{KwGoTo}{go to}
\SetKwProg{Fn}{Function}{:}{}
\Fn{{\sc Expand}($V,E,\mathcal{D},\mathcal{A}$,$B$,$k$)}{
    let $L \gets \{\}$\;
    \ForEach{$X, Y$ where $X \to Y \notin E \cup B $ and $Y \to X \notin E \cup B$}{
        let $\mathbf{Z}$ be a set that $d$-separates $X$ and $Y$ in $(V,E)$\;
        \If{$\mathcal{D}(X, Y, \mathbf{Z}) = 0$}{
	    $L \gets L \cup \mathcal{A}(X, Y) $ \;
        }
	\If{$|L|\geq k$}{\KwGoTo 12\;}
    }
    $ R \gets \textsc{FixCycles}(V, E \cup L, \mathcal{D}) $ \; 
    $ B \gets B \cup R \; ; \;  E \gets (E \cup L) \setminus R$ \;
    \Return{$(V,E,B)$}\;
}
\caption{Adding edges based on data and domain knowledge.}
\label{algo:expand}
\end{algorithm}

@@

\begin{proof}
For an edge $X \to Y$ in the skeleton of $G$, 
$\mathcal{D}_G(X, Y, \mathbf{Z}) = 0$ regardless 
of $\mathbf{Z}$, so all edges in the skeleton are 
retained after {\sc Prune}. Conversely, if 
 $X \to Y$ is not in the skeleton of $G$, let 
$\mathbf{Z}$ be the $d$-separating set chosen 
in line~5 of {\sc Prune} (there is at least one 
such $\mathbf{Z}$, the union of the parents of 
$X$ and $Y$). Since  $\mathbf{Z}$ $d$-separates 
all paths from $X$ to $Y$ in $G'$, it does the same 
in $G$ which contains a subset of these paths. 
Therefore, all edges not in the skeleton of $G$ are 
removed.
\end{proof}

>>>>

\begin{algorithm}[h]
\DontPrintSemicolon
\SetAlgoLined
\SetKwFunction{Expand}{Expand}
\SetKw{KwGoTo}{go to}
\SetKwProg{Fn}{Function}{:}{}
\Fn{{\sc Expand}($V,E,\mathcal{D},\mathcal{A}$,$B$,$k$)}{
    $L \gets \{\}$\;
    \ForEach{$X, Y$ where $X \to Y \notin E \cup B $ and $Y \to X \notin E \cup B$}{
        let $\mathbf{Z}$ be a set that $d$-separates $X$ and $Y$ in $(V,E)$\;
        \If{$\mathcal{D}(X, Y, \mathbf{Z}) = 0$}{
	    $L \gets L \cup \mathcal{A}(X, Y) $ \;
        }
	\If{$|L|\geq k$}{\KwGoTo 12\;}
    }
    $ R \gets \textsc{FixCycles}(V, E \cup L, \mathcal{D}) $ \; 
    $ B \gets B \cup R \; ; \;  E \gets (E \cup L) \setminus R$ \;
    \Return{$(V,E,B)$}\;
}
\caption{Adding edges based on data and domain knowledge.}
\label{algo:expand}
\end{algorithm}

@@

\begin{proof}
For an edge $X \to Y$ in the skeleton of $G$, 
$\mathcal{D}_G(X, Y, \mathbf{Z}) = 0$ regardless 
of $\mathbf{Z}$, so all edges in the skeleton are 
retained after {\sc Prune}. Conversely, if 
 $X \to Y$ is not in the skeleton of $G$, let 
$\mathbf{Z}$ be the $d$-separating set chosen 
in line~4 of {\sc Prune} (there is at least one 
such $\mathbf{Z}$, the union of the parents of 
$X$ and $Y$). Since  $\mathbf{Z}$ $d$-separates 
all paths from $X$ to $Y$ in $G'$, it does the same 
in $G$ which contains a subset of these paths. 
Therefore, all edges not in the skeleton of $G$ are 
removed.
\end{proof}
